New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-09-23 paper/paper.Rmd
added some sentences about manual slice

One might implement such an interactive interface via R Shiny, but in particular the tracking of the mouse position in small increments might pose a challenge. Here we found the dynamic graphics interface from Mathematica to be especially useful. In the following we first describe the relevant Mathematica functionalities and how they were used in the implementation, followed by a brief sketch of how the new approach might be implemented in the `tourr` package.

@@

The R package tourr [@tourr] provides numerous types of tours. An additional function, `radial_tour()` has been constructed that will generate a sequence of projections that will decrease the coordinates for $V_m$ to $\boldsymbol{0}$ and back to the original values. It is applicable for any projection dimension, $d$.

Changing slice center

@@

The source material and animated gifs for this paper are available at

Mathematica notebook

Appendix

>>>>

One might implement such an interactive interface via R Shiny, but in particular the tracking of the mouse position in small increments might pose a challenge. Here we found the dynamic graphics interface from Mathematica to be especially useful. In the following we first describe the relevant Mathematica functionalities and how they were used in the implementation, followed by a brief sketch of how the new approaches are implemented in the `tourr` package.

@@

The R package tourr [@tourr] provides numerous types of tours. An additional function, `radial_tour()` has been constructed that will generate a sequence of projections that will decrease the coordinates for $V_m$ to $\boldsymbol{0}$ and back to the original values. It is applicable for any projection dimension, $d$. Changing slice center manually can be accomplished with the new function, `manual_slice()`. This changes the value of the center point ($\mathbf{c}$) of the slice, along a selected variable axis. It slices from the center of the data out to one side, back to the center, out to the opposite side, and then back to the center.

@@

The source material and animated gifs for this paper are available at [https://github.com/uschiLaa/mmtour](https://github.com/uschiLaa/mmtour).

The supplementary materials include:

- Two Mathematica notebooks, one focused on the application, and another that could be used generically for new data.
- Appendix with additional details about manual controls, and Mathematica functions.
- Animated gifs illustrating the manual tour and slicing, matching the static figures in the paper. These are also available at https://vimeo.com/747585410 and https://vimeo.com/747590472.

### 2022-09-23 paper/paper.tex
tinkered with scatterplot matrix
added some sentences about manual slice

One might implement such an interactive interface via R Shiny, but in
particular the tracking of the mouse position in small increments might
pose a challenge. Here we found the dynamic graphics interface from
Mathematica to be especially useful. In the following we first describe
the relevant Mathematica functionalities and how they were used in the
implementation, followed by a brief sketch of how the new approach might
be implemented in the \texttt{tourr} package.

@@

The R package tourr \citep{tourr} provides numerous types of tours. An
additional function, \texttt{radial\_tour()} has been constructed that
will generate a sequence of projections that will decrease the
coordinates for \(V_m\) to \(\boldsymbol{0}\) and back to the original
values. It is applicable for any projection dimension, \(d\).

Changing slice center

@@

{\centering \includegraphics[width=0.8\linewidth]{paper_files/figure-latex/penguins-scatmat-1}

@@

The source material and animated gifs for this paper are available at

Mathematica notebook

Appendix

>>>>

One might implement such an interactive interface via R Shiny, but in
particular the tracking of the mouse position in small increments might
pose a challenge. Here we found the dynamic graphics interface from
Mathematica to be especially useful. In the following we first describe
the relevant Mathematica functionalities and how they were used in the
implementation, followed by a brief sketch of how the new approaches are
implemented in the \texttt{tourr} package.

@@

The R package tourr \citep{tourr} provides numerous types of tours. An
additional function, \texttt{radial\_tour()} has been constructed that
will generate a sequence of projections that will decrease the
coordinates for \(V_m\) to \(\boldsymbol{0}\) and back to the original
values. It is applicable for any projection dimension, \(d\). Changing
slice center manually can be accomplished with the new function,
\texttt{manual\_slice()}. This changes the value of the center point
(\(\mathbf{c}\)) of the slice, along a selected variable axis. It slices
from the center of the data out to one side, back to the center, out to
the opposite side, and then back to the center.

@@

{\centering \includegraphics[width=0.6\linewidth]{paper_files/figure-latex/penguins-scatmat-1}

@@

The source material and animated gifs for this paper are available at
\url{https://github.com/uschiLaa/mmtour}.

The supplementary materials include:

\begin{itemize}
\tightlist
\item
  Two Mathematica notebooks, one focused on the application, and another
  that could be used generically for new data.
\item
  Appendix with additional details about manual controls, and
  Mathematica functions.
\item
  Animated gifs illustrating the manual tour and slicing, matching the
  static figures in the paper. These are also available at
  \url{https://vimeo.com/747585410} and
  \url{https://vimeo.com/747590472}.
\end{itemize}
